Rank-based Training-Free NAS Algorithm

### 2023-06-11 paper/main.tex
update paper

% what is unknown?
    % table放第一頁 不然就不要放
    % 做成圖表放第一頁
    However, \xtab{table:corr_score} shows most of score functions suffer from low correlation between 
    score values and the final accuracy of architectures, leading to a predicament 
    that no matter how good the search method is used, we can hardly find 
    an optimal architecture. 
    The major problem causes the low correlation is that a single score 
    function can only evaluate one perspect/characteristic of an architecture. 
    \begin{table}[tb]
        \caption{\textsc{The Kendall correlation between training-free score and test accuracy, evaluated on the three datasets of NATS-Bench \cite{Dong_2021}. 
        Each metric has been computed three times with different initialisations and the average is taken as final score.}}
        \resizebox{0.48\textwidth}{!}{
            \begin{tabular}{cccc}\toprule
                Training-free score function & CIFAR-10 & CIFAR-100 & ImageNet-16-120 \\ 
                \midrule
                \bf{NTK}                     & -0.33    & -0.30     & -0.39 \\
                \bf{Snip}                    & 0.45     & 0.47      & 0.41  \\
                \bf{Fisher}                  & 0.39     & 0.40      & 0.36  \\
                \bf{Grasp}                   & 0.28     & 0.35      & 0.35  \\
                \bf{NASWOT}                  & 0.61     & 0.62      & 0.60  \\
                \bf{SynFlow}                 & 0.57     & 0.56      & 0.56  \\
                \bf{LogSynFlow}              & 0.61     & 0.60      & 0.59  \\
                \bf{Rank-Based (ours)}       & X        & X         & X     \\ \bottomrule
                \label{table:corr_score}
            \vspace{-\baselineskip}
            \end{tabular}
        }
    \end{table}
    \begin{figure*}[b]
        \vspace{-\baselineskip}
        \resizebox{1.0\textwidth}{!}{\includegraphics{asset/naswot.pdf}}
        \caption{A simple example to illustrate the procedure of NASWOT.}
        \label{fig:naswot}
        \centering
        \vspace{-\baselineskip}
    \end{figure*}
% method
    To address the problem, we propose cooperating three complement score 
    functions by ranking, which allows every score functions evaluate an 
    architecture without losing fairness. 
    The first score function is noise immunity (NI) \cite{10092788}, as 
    an indicator of the ability to distinguish two images. 
    The second one is NASWOT, as score to estimate the ability of expression 
    of an architecture and also a complement of NI. 
    The last one is SNIP used as the measurement of trainability and 
    also as a complement to NI and NASWOT. 
    With these three complement score functions, an evaluation of an 
    architecture is not simply from a single aspect but three different 
    aspects, which is like estimate the weight of an object by not only 
    the length but its height and width. 
    %compares the different search algorithms for NAS, e.g., random search, genetic 
    %algorithm (GA) \cite{mitchell1998introduction}, simulated annealing algorithm (SA)
    %\cite{kirkpatrick1983optimization}.

@@

    % ni 對圖描述多一點
    Wu et al. \cite{10092788} found, in some case, an architecture with high 
    NASWOT score may classify the same kind of input data into different classes. 
    To fix this defect, Wu et al. proposed using noise immunity (NI) to 
    evaluate an architecture. \xfig{fig:ni} gives an example to illustrate how 
    noise immunity evaluate an architecture. The score function picks a 
    mini-batch of data, denoted $X$, and then applies Gaussion noise on it. 
    The process can be defined by $X'=X+z$ where $z$ is the Gaussion noise. 
    By passing $X$ and $X'$ through the untrained architecture, then computing 
    the difference of square of each feature maps captured at all pooling layers, 
    denoted $\eta$. According to the fact that the input data are the same kind, 
    the small $\eta$ the better the noise immunity of the architecture is.

@@

    % synflow
    % 再調
    Besides from these two image-related aspects, there is another aspect to evaluate  
    a network. 
    \textit{The Lottery Ticket Hypothesis} \cite{frankle2019lottery}, reveals that a 
    network may have a "core" which decides the final accuracy of the network. 
    How to pruning a network correctly is therefore tempting. Lee et al. 
    \cite{lee2019snip} proposed to use connection sensitivity as a criterion to prune 
    the network which can be briefly viewed as 
    \begin{equation}
        \label{equ:snip_connection_sensitivity}
        s_j=\lvert w_j\frac{\partial L}{\partial w_j}\rvert,
    \end{equation}
    where $\textbf{w}$ is the weight of the netwrok, $w_j$ the $j$-th element of 
    $\textbf{w}$. The meaning behind is to approximate the contribution 
    to the change of the loss function from a specific connection. By pruning the 
    connections which has relatively small contribution, the expensive prune, retrain 
    cycles, can be prevented. 
    Later, Wang et al. \cite{wang2020picking} noticed that SNIP with a high pruning ratio 
    tends to cause layer-collapse, which prune all parameters in a single weight layer. 
    Therefore, they propose to approximate the change in gradient norm which defined as 
    \begin{equation}
        \label{equ:grap}
        S_p(\bf{\theta})=-(H\frac{\partial \mathcal L}{\partial \bf{\theta}})\odot\bf{\theta},
    \end{equation}
    where $H$ is the Hessian matrix, $\bf{\theta}$ the parameters, and $\odot$ is Hadamard product. 
    In \cite{tanaka2020pruning}, Tanaka et al. generalized the synaptic saliency scores as 
    \begin{equation}
        \label{equ:synflow}
        S_p(\theta)=\frac{\partial \mathcal L}{\partial \theta}\odot\theta,
    \end{equation}
    which is named SynFlow. 
    Abdelfattah et al. \cite{abdelfattah2021zerocost} extended the work, conclude that summing 
    synaptic saliency score over all parameters in the model can be used to score a network 
    architecture, which is formula as 
    \begin{equation}
        \label{equ:zero_cost}
        S_n=\sum^N_i S_p(\theta)_i
    \end{equation}
    Finally, Cavagnero et al. \cite{Cavagnero_2023} imporved SynFlow, which is likely to fall into 
    gradient explosion problem, and proposed LogSynFlow score function, simply scaling down the gradient. 
    The formula is defined by 
    \begin{equation}
        \label{equ:logsynflow}
        S(\theta)=\theta\cdot\log(\frac{\partial \mathcal L}{\partial \theta}+1)
    \end{equation}

@@

    \section{Methods}
    \label{sec:proposed}
    \subsection{Motivation}
    The motivation origins from these three questions:

@@

    As mentioned, the key is to choose the complement of a score function. For example, 
    NASWOT and NI. And for NASWOT and NI, which are both description of the ability of 
    the graphic recognition of an architecture. The complement of them can be a measurement 
    of trainability, e.g., SynFlow, NTK, which means whether this architecture is easy to 
    train or not.

    \subsection{Rank-Based Score Function}
    \begin{algorithm}[h]
        \caption{The Rank Algorithm}\label{alg:rank-based}
        \begin{algorithmic}[1]
            \Input ${\mathbb N}^{s}\subset{\mathbb N}^{*}$
            \For{$\text{each }{\mathbb N}^i\text{ in }{\mathbb N}^s$}
                \For{$\text{each }j\in\{1,\ldots,M\}$}
                    \State $s_{{\mathcal F}_{j}}({\mathbb N}^i)={\mathcal F}_{j}({\mathbb N}^i)$
                \EndFor
            \EndFor
            \For{$\text{each }j\in\{1,\ldots,M\}$}
                \State $r_{{\mathcal F}_{j}}({\mathbb N}^i)$ = index of ${\mathbb N}^i$ in list $[s_{{\mathcal F}_{j}}({\mathbb N}^1),\ldots,s_{{\mathcal F}_{j}}({\mathbb N}^{\lvert {\mathbb N}^s\rvert})]$ \par sorted by descending order
            \EndFor
            \State $r({\mathbb N}^i)=\sum^M_{j=0} r_{{\mathcal F}_{j}}({\mathbb N}^i)$
            \State $i^*=\arg\min_{i}\{r({\mathbb N}^i)\}$
            \State $\textbf{Return }{\mathbb N}^{i^*}$
        \end{algorithmic}
    \end{algorithm}

    The proposed rank-based score function is outlined in \xalg{alg:rank-based}. The first step is to evaluate the 
    network architectures in the subset, denoted $\mathbb N^s$, of search space, denoted $\mathbb N^*$. The evaluation 
    of an architecture determined by $j$-th score function is denoted $s_{\mathcal F_j}(\mathbb N^i)$. After evaluating 
    the subset of search space, the rank of each score function is calculated, denoted $r_{\mathcal F}$. Then the final 
    rank, $r$, calculated by summing up the ranks. 
    If a network architecture gains higher score in these score functions, the final rank should be higher (smaller index) too. 
    Therefore, the highest (minimum) rank in $r$ shall be the best network architecture. In summary, the rank-based score 
    function makes the contribution of each score function even.

@@

    \begin{figure*}[htb]
        \centering
        \hspace*{-\baselineskip}
        \vspace*{-\baselineskip}
        \includegraphics[]{asset/SA.pdf}
        \caption{A simple example to illustrate an iteration of SA with Rank-based score function.}
        \label{fig:SA}
    \end{figure*}

    \xfig{fig:SA} illustrates how SA with rank-based score function works in an iteration.

    \section{experiment result}
    \label{sec:results}

    \subsection*{natsbenchsss}
    The result of natsbenchsss is shown in \xtab{table:overall_sss}.
    \begin{table*}[htb]
        %\normalsize
        %\centering
        \newcommand{\z}{\phantom{0}}
        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms.}}
          \vspace{-\baselineskip}
        \begin{tabular}{@{}lccccccl@{}}\toprule
        Method & Search (s) & \multicolumn{2}{c}{CIFAR-10} & \multicolumn{2}{c}{CIFAR-100} & \multicolumn{2}{c}{ImageNet-16-120} \\ \cmidrule(lr){3-4}\cmidrule(lr){5-6}\cmidrule(lr){7-8}
        & & validation & test & validation & test & validation & test \\ \midrule
        &&&&\textbf{Non-weight sharing}&&&\\
        AREA      & $12,000$ & $84.62 \pm \z{0.41}$                & $93.16 \pm 0.16$               & $59.24 \pm \z{1.11}$                 & $69.56 \pm \z{0.96}$                & $37.58 \pm 1.09$                 & $45.30 \pm \z{0.91}$                \\
        REA       & $12,000$ & $90.26 \pm \z{0.22}$                & $93.17 \pm 0.21$               & $69.48 \pm \z{0.76}$                 & $69.49 \pm \z{0.94}$                & $44.84 \pm 0.72$                 & $45.47 \pm \z{0.91}$                \\
        RS        & $12,000$ & $90.08 \pm \z{0.24}$                & $93.01 \pm 0.29$               & $69.14 \pm \z{0.94}$                 & $69.17 \pm \z{1.00}$                & $44.66 \pm 1.02$                 & $44.83 \pm \z{1.05}$                \\
        RL        & $12,000$ & $90.17 \pm \z{0.23}$                & $93.08 \pm 0.21$               & $69.23 \pm \z{0.87}$                 & $69.29 \pm \z{1.08}$                & $44.68 \pm 0.91$                 & $45.05 \pm \z{0.93}$                \\
        BOHB      & $12,000$ & $90.05 \pm \z{0.30}$                & $93.03 \pm 0.20$               & $69.04 \pm \z{0.76}$                 & $69.16 \pm \z{0.90}$                & $44.71 \pm 0.78$                 & $44.91 \pm \z{1.05}$                \\ \midrule
        %&& Search (s) & test & Search(s) & test & Search(s) & test \\ \midrule
        &&&&\textbf{Training-free}&&&\\
        NI (N=1,000) & $X$ & $89.56\pm \z{0.147}$ & $92.55\pm 0.187$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
        NASWOT (N=1,000) & $X$ & $89.25\pm \z{0.412}$ & $92.21\pm 0.298$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
        logsynflow (N=1,000) & $X$ & $89.61\pm \z{0.101}$ & $92.60\pm 0.188$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
        rk (N=1000) & $X$ & $89.59\pm \z{0.136}$ & $92.51\pm 0.171$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
        GA-rk & $457.54$ & $90.29\pm \z{0.149}$ & $93.27\pm0.193$ & $69.88\pm \z{0.497}$ & $70.06\pm \z{0.481}$ & $45.57\pm 0.425$ & $46.19\pm \z{0.846}$ \\ 
        SA-rk & $682.36$ & $90.37\pm \z{0.204}$ & $93.29\pm0.182$ & $70.11\pm \z{0.457}$ & $70.32\pm \z{0.458}$ & $45.38\pm 0.499$ & $46.45\pm \z{0.687}$ \\ \bottomrule
        \end{tabular}
        \label{table:overall_sss}
          \vspace{-\baselineskip}
      \end{table*}

    \subsection*{nasbench201}
    The result of nasbench201 is shown in \xtab{table:overall_201}.

@@

        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms.}}

@@

        \begin{tabular}{@{}lccccccl@{}}\toprule

@@

        AREA      & $12,000$ & $91.18 \pm \z{0.43}$                & $93.95 \pm \z{0.39}$               & $71.84 \pm \z{1.21}$                 & $71.92 \pm \z{1.29}$                & $45.04 \pm 1.03$                 & $45.40 \pm \z{1.14}$                \\
        REA       & $12,000$ & $91.08 \pm \z{0.54}$                & $93.89 \pm \z{0.50}$               & $71.69 \pm \z{1.34}$                 & $71.83 \pm \z{1.33}$                & $44.96 \pm 1.41$                 & $45.30 \pm \z{1.51}$                \\
        RS        & $12,000$ & $90.91 \pm \z{0.33}$                & $93.67 \pm \z{0.33}$               & $70.91 \pm \z{1.04}$                 & $70.99 \pm \z{0.99}$                & $44.52 \pm 0.99$                 & $44.56 \pm \z{1.25}$                \\
        RL        & $12,000$ & $90.87 \pm \z{0.41}$                & $93.63 \pm \z{0.36}$               & $70.62 \pm \z{1.08}$                 & $70.77 \pm \z{1.05}$                & $44.20 \pm 1.22$                 & $44.23 \pm \z{1.37}$                \\
        BOHB      & $12,000$ & $88.47 \pm \z{1.19}$                & $91.79 \pm \z{1.11}$               & $67.18 \pm \z{2.05}$                 & $67.50 \pm \z{2.05}$                & $38.94 \pm 3.58$                 & $39.00 \pm \z{3.73}$                \\ \midrule

@@

        RSWS      & $\z{4,154}$  & $76.95 \pm 16.74$                & $82.60 \pm 12.10$               & $52.51 \pm 18.33$                & $52.93 \pm 18.32$                   & $29.76 \pm 9.50$                 & $29.16 \pm 9.61$               \\
        DARTS-V1  & $\z{5,475}$  & $39.77 \pm \z{0.00}$                & $54.30 \pm \z{0.00}$               & $15.03 \pm \z{0.00}$                 & $15.61 \pm \z{0.00}$                & $16.43 \pm 0.00$                 & $16.32 \pm \z{0.00}$                \\

>>>>

% what is unknown?
    % table放第一頁 不然就不要放
    % 做成圖表放第一頁
    However, \xtab{table:corr_score} shows most of score functions suffer from low correlation between 
    score values and the final accuracy of architectures, leading to a predicament 
    that no matter how good the search method is used, we can hardly find 
    an optimal architecture. 
    The major problem causes the low correlation is that a single score 
    function can only evaluate one perspect/characteristic of an architecture. 
    \begin{table}[tb]
        \caption{\textsc{The Kendall correlation between training-free score and test accuracy, evaluated on the three datasets of NATS-Bench \cite{Dong_2021}. 
        Each metric has been computed three times with different initialisations and the average is taken as final score.}}
        \resizebox{0.48\textwidth}{!}{
            \begin{tabular}{cccc}\toprule
                Training-free score function & CIFAR-10 & CIFAR-100 & ImageNet-16-120 \\ 
                \midrule
                \bf{NTK}                     & -0.33    & -0.30     & -0.39 \\
                \bf{Snip}                    & 0.45     & 0.47      & 0.41  \\
                \bf{Fisher}                  & 0.39     & 0.40      & 0.36  \\
                \bf{Grasp}                   & 0.28     & 0.35      & 0.35  \\
                \bf{NASWOT}                  & 0.61     & 0.62      & 0.60  \\
                \bf{SynFlow}                 & 0.57     & 0.56      & 0.56  \\
                \bf{LogSynFlow}              & 0.61     & 0.60      & 0.59  \\
                \bf{Rank (ours)}             & X        & X         & X     \\ \bottomrule
                \label{table:corr_score}
            \vspace{-\baselineskip}
            \end{tabular}
        }
    \end{table}
    \begin{figure*}[b]
        \vspace{-\baselineskip}
        \resizebox{1.0\textwidth}{!}{\includegraphics{asset/naswot.pdf}}
        \caption{A simple example to illustrate the procedure of NASWOT.}
        \label{fig:naswot}
        \centering
        \vspace{-\baselineskip}
    \end{figure*}
% method
    To address the problem, we propose cooperating three complement score 
    functions by ranking, which allows every score functions evaluate an 
    architecture without losing fairness. 
    The first score function is noise immunity (NI) \cite{10092788}, as 
    an indicator of the ability to distinguish two images. 
    The second one is NASWOT, as score to estimate the ability of expression 
    of an architecture and also a complement of NI. 
    The last one is SNIP used as the measurement of trainability and 
    also as a complement to NI and NASWOT. 
    With these three complement score functions, an evaluation of an 
    architecture is not simply from a single aspect but three different 
    aspects, which is like estimate the weight of an object by not only 
    the length but its height and width. 
    %compares the different search algorithms for NAS, e.g., random search, genetic 
    %algorithm (GA) \cite{mitchell1998introduction}, simulated annealing algorithm (SA)
    %\cite{kirkpatrick1983optimization}.

@@

    % ni 對圖描述多一點
    Wu et al. \cite{10092788} found, in some case, an architecture with high 
    NASWOT score may classify the same kind of input data into different classes. 
    To fix this defect, Wu et al. proposed using noise immunity (NI) to 
    evaluate an architecture. \xfig{fig:ni} gives an example to illustrate how 
    noise immunity evaluate an architecture. The score function picks a 
    mini-batch of data, denoted $X$, and then applies Gaussion noise on it. 
    The process can be defined by $X'=X+z$ where $z$ is the Gaussion noise. 
    By passing $X$ and $X'$ through the untrained architecture, then computing 
    the difference of square of each feature maps captured at all pooling layers, 
    denoted $\eta$. More specifically, first, calculate the matrix $\kappa$ defined by 
    \begin{equation}
        \label{equ:ni_kappa}
        \kappa=\begin{pmatrix}\frac{(\tau_{1,1}-\tau'_{1,1})^2}{\lvert \tau_{1,1}\rvert}&\cdots&\frac{(\tau_{1,N}-\tau'_{1,N})^2}{\lvert \tau_{1,N}\rvert}\\\vdots&\ddots&\vdots\\\frac{(\tau_{L,1}-\tau'_{L,1})^2}{\lvert \tau_{L,1}\rvert}&\cdots&\frac{(\tau_{L,N}-\tau'_{L,N})^2}{\lvert \tau_{L,N}\rvert}\end{pmatrix},
    \end{equation}
    where $L$ is the total number of pooling layers; $N$ the size of mini-batch, 
    and $\tau_{i,j}$ and $\tau'_{i,j}$ are the feature maps which $X$ passing and 
    the one perturbed by $X'$ at the $i$-th pooling layer and $j$-th input 
    data of the mini-batch, respectively. 
    Then $\eta$ can be calculated by 
    \begin{equation}
        \label{equ:ni_eta}
        \eta=\ln(\epsilon+e_L\kappa e_N),
    \end{equation}
    where $\epsilon$ is a small positive number, and $e_L$ and $e_N$ are a row 
    vector of 1's of size $L$ and a column vector of 1's of size $N$, respectively. 
    According to the fact that the input data are the same kind, the smaller $\eta$ 
    is, the better the noise immunity of the architecture is.

@@

    % synflow
    % 再調
    Besides from these two image-related aspects, there is another aspect to evaluate  
    a network. 
    \textit{The Lottery Ticket Hypothesis} \cite{frankle2019lottery}, reveals that a 
    network may have a "core" which decides the final accuracy of the network. 
    How to pruning a network correctly is therefore tempting. Lee et al. 
    \cite{lee2019snip} proposed to use connection sensitivity as a criterion to prune 
    the network which can be briefly viewed as 
    \begin{equation}
        \label{equ:snip_connection_sensitivity}
        s_j=\lvert \frac{\partial \mathcal L}{\partial w_j}w_j\rvert,
    \end{equation}
    where $\textbf{w}$ is the weight of the netwrok, $w_j$ the $j$-th element of 
    $\textbf{w}$, and $\mathcal L$ is the empirical risk. The meaning behind is to approximate the contribution 
    to the change of the loss function from a specific connection. By pruning the 
    connections which has relatively small contribution, the expensive prune, retrain 
    cycles, can be prevented. 
    Later, Wang et al. \cite{wang2020picking} noticed that SNIP with a high pruning ratio 
    tends to cause \textit{layer-collapse}, which prunes all parameters in a single weight 
    layer. Therefore, they propose Gradient Signal Preservation (GraSP) algorithm, which 
    aims to preserve the gradient flow at initialization by approximating the change in 
    gradient norm defined as 
    \begin{equation}
        \label{equ:grap}
        S_p(\theta)=-(\textbf{H}\frac{\partial \mathcal L}{\partial \theta})\odot\theta,
    \end{equation}
    where $\textbf{H}$ is the Hessian matrix, $\theta$ the parameters, and $\odot$ is Hadamard product. 
    In \cite{tanaka2020pruning}, to solve the problem that the existing pruning algorithms, e.g., 
    Magnitude, SNIP, GraSP, using global-masking usually encounter layer-collapse which will make 
    the pruned network untrainable. 
    Tanaka et al. generalized the synaptic saliency scores as 
    \begin{equation}
        \label{equ:synflow}
        S_p(\theta)=\frac{\partial \mathcal R}{\partial \theta}\odot\theta,
    \end{equation}
    where $\mathcal R$ is a scalar loss function, and proposed Iterative Synaptic Flow Pruning (SynFlow) 
    algorithm which is an extension of magnitude pruning algorithm and avoids layer-collapse. 
    Abdelfattah et al. \cite{abdelfattah2021zerocost} extended the work, proposed to score a 
    network by summing the synaptic saliency score over all parameters in the model, which is 
    defined as 
    \begin{equation}
        \label{equ:zero_cost}
        S_n=\sum^N_i S_p(\theta)_i.
    \end{equation}
    The rationale behind is to calculate all the contribution to the loss function of parameters. 
    The higher the score of an architecture, the more trainable this architecture is. 
    Finally, Cavagnero et al. \cite{Cavagnero_2023} imporved SynFlow, which is likely to fall into 
    gradient explosion problem, and proposed LogSynFlow which simply scaling down the gradient. 
    The formula is defined by 
    \begin{equation}
        \label{equ:logsynflow}
        S(\theta)=\theta\cdot\log(\frac{\partial \mathcal L}{\partial \theta}+1)
    \end{equation}

@@

    \section{Methods}
    \label{sec:proposed}

    \subsection{Motivation}
    The motivation origins from these three questions:

@@

    As mentioned, the key is to choose the complement of a score function. For example, 
    NASWOT and NI. And for NASWOT and NI, which are both description of the ability of 
    the graphic recognition of an architecture. The complement of them can be a measurement 
    of trainability, e.g., SynFlow, NTK, which means whether this architecture is easy to 
    train or not. In this paper, NI, NASWOT, and LogSynFlow are used in the ranking algorithm.

    \subsection{The Ranking Algorithm}
    \begin{algorithm}[h]
        \caption{The Ranking Algorithm}\label{alg:rank-based}
        \begin{algorithmic}[1]
            \Input{a subspace, ${\mathbb N}^{s}$, from search space, ${\mathbb N}^{*}$}
            \For{$\text{each }{\mathbb N}^i\text{ in }{\mathbb N}^s$}
                \For{$\text{each }j\in\{1,\ldots,M\}$}
                    \State $s_{{\mathcal F}_{j}}({\mathbb N}^i)={\mathcal F}_{j}({\mathbb N}^i)$
                \EndFor
            \EndFor
            \For{$\text{each }j\in\{1,\ldots,M\}$}
                \State $r_{{\mathcal F}_{j}}({\mathbb N}^i)$ = index of ${\mathbb N}^i$ in list $[s_{{\mathcal F}_{j}}({\mathbb N}^1),\ldots,s_{{\mathcal F}_{j}}({\mathbb N}^{\lvert {\mathbb N}^s\rvert})]$ \par sorted by descending order
            \EndFor
            \State $r({\mathbb N}^i)=\sum^M_{j=0} r_{{\mathcal F}_{j}}({\mathbb N}^i)$
            %\State $i^*=\arg\min_{i}\{r({\mathbb N}^i)\}$
            %\State $\textbf{Return }{\mathbb N}^{i^*}$
            \State $\textbf{Return }r$
        \end{algorithmic}
    \end{algorithm}

    The proposed ranking algorithm is outlined in \xalg{alg:rank-based}. 
    The first step is to evaluate the network architectures in the subset, 
    denoted $\mathbb N^s$, of search space, denoted $\mathbb N^*$. The 
    evaluation of an architecture determined by $j$-th score function is 
    denoted $s_{\mathcal F_j}(\mathbb N^i)$. After evaluating the subset 
    of search space, the rank of each score function is calculated, denoted 
    $r_{\mathcal F}$. Then the final rank, $r$, calculated by summing up 
    the ranks. If a network architecture gains higher score in these score 
    functions, the final rank should be higher (smaller index) too. Therefore, 
    the highest (minimum) rank in $r$ shall be the best network architecture. 
    In summary, the rank-based score function makes the contribution of 
    each score function even, and therefore evaluate an architecture from 
    different aspects. In this paper, NI and NASWOT are used as a complement 
    set, which take the ability of images generalization and distinction. 
    Lastly, LogSynFlow complements NI and NASWOT which takes the trainability 
    into account.

@@

    \begin{algorithm}[h]
        \caption{The Simulated Annealing with Ranking Algorithm}\label{alg:SA}
        \begin{algorithmic}[1]
            \Input{search space $\mathbb N^*$, initial temperature $T$, ending temperature $\tau$, 
            a real number between 0 and 1, $\alpha$, the number of iteration, $I$}
            \State $s^*=s=\text{sample a random architecture from }\Bbb N^*$
            \While{$T>\tau$}
                \For{$\text{ each }i \in [1\ldots I]$}
                    \State $r=\text{Ranking}(\{s\}\cup U(s))$ \Comment{Ranking $s$ with the neighbourhood of $s$, denoted $U(s)$}
                    \State $s^*=\arg\min\{r(\Bbb N^i)\}$ \Comment{Update the expected best algorithm}
                    \State $\Delta E=r(s^*)-r(s)$
                    \State $x\sim \mathcal U(0,1)$ \Comment{Sample $x$ from a uniform distribution between 0 and 1}
                    \If{$x\geq e^{\frac{\Delta E}{T}}$} \Comment{Accept by probability}
                        \State $s\leftarrow s^*$
                    \EndIf
                \EndFor
                \State $T\leftarrow T\times \alpha$
            \EndWhile
            \State $\textbf{Return }s^*$ \Comment{Return the best architecture}
        \end{algorithmic}
    \end{algorithm}

    The modified version of the simulated annealing algorithm with ranking algorithm 
    is outlined in \xalg{alg:SA}. The first step is to sample a architecture, denoted 
    $s$, from search space. Then use $s$ as a "seed" to generate the neighbourhood of it, 
    applying ranking algorithm on the neighbourhood, $\{s\}\cup U(s)$. After ranking, 
    the expected best architecture can be determined and update, but the seed for next 
    iteration will be replaced by $s^*$ according to probability, $e^{\frac{\Delta E}{T}}$.
    After the $I$ iterations, the temperature scales down by $\alpha$. The algorithm 
    is done when $T\leq\tau$, and the best architecture will be retruned.

    %\begin{figure*}[htb]
    %    \centering
    %    \hspace*{-\baselineskip}
    %    \vspace*{-\baselineskip}
    %    \includegraphics[]{asset/SA.pdf}
    %    \caption{A simple example to illustrate an iteration of SA with Rank-based score function.}
    %    \label{fig:SA}
    %\end{figure*}
    %\xfig{fig:SA} illustrates how SA with rank-based score function works in an iteration.

    \section{experiment result}
    \label{sec:results}
    \subsection{Environment and Parameter Settings}
    The experiment is conducted on a PC with Intel Core i7-11700K (3.60 GHz, 16-MB Cache, and 16 cores), 
    a single NVIDIA RTX3070 Ti GPU with 8 GB memory, driver version 520.61.05, CUDA version 11.8, and 
    65 GB available memory running on Ubuntu 20.04.1 with linux kernel 5.15.0-73-generic. All the program 
    is written in Python 3.7.16 with PyTorch 1.7.1+cu110 package. 
    \subsection{NATS-bench-SSS}
    The result of NATS-bench-SSS is shown in \xtab{table:overall_sss}.
    \begin{table*}[htb]
        %\normalsize
        %\centering
        \newcommand{\z}{\phantom{0}}
        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms in NATS-Bench-SSS.}}
          \vspace{-\baselineskip}
        \begin{tabular}{@{}lccccccc@{}}\toprule
        Method & Search (s) & \multicolumn{2}{c}{CIFAR-10} & \multicolumn{2}{c}{CIFAR-100} & \multicolumn{2}{c}{ImageNet-16-120} \\ \cmidrule(lr){3-4}\cmidrule(lr){5-6}\cmidrule(lr){7-8}
        & & validation & test & validation & test & validation & test \\ \midrule
        &&&&\textbf{Non-weight sharing}&&&\\
        AREA      & $12,000$ & $84.62 \pm \z{0.41}$                & $93.16 \pm 0.16$               & $59.24 \pm \z{1.11}$                 & $69.56 \pm \z{0.96}$                & $37.58 \pm 1.09$                 & $45.30 \pm \z{0.91}$                \\
        REA       & $12,000$ & $90.26 \pm \z{0.22}$                & $93.17 \pm 0.21$               & $69.48 \pm \z{0.76}$                 & $69.49 \pm \z{0.94}$                & $44.84 \pm 0.72$                 & $45.47 \pm \z{0.91}$                \\
        RS        & $12,000$ & $90.08 \pm \z{0.24}$                & $93.01 \pm 0.29$               & $69.14 \pm \z{0.94}$                 & $69.17 \pm \z{1.00}$                & $44.66 \pm 1.02$                 & $44.83 \pm \z{1.05}$                \\
        RL        & $12,000$ & $90.17 \pm \z{0.23}$                & $93.08 \pm 0.21$               & $69.23 \pm \z{0.87}$                 & $69.29 \pm \z{1.08}$                & $44.68 \pm 0.91$                 & $45.05 \pm \z{0.93}$                \\
        BOHB      & $12,000$ & $90.05 \pm \z{0.30}$                & $93.03 \pm 0.20$               & $69.04 \pm \z{0.76}$                 & $69.16 \pm \z{0.90}$                & $44.71 \pm 0.78$                 & $44.91 \pm \z{1.05}$                \\ \midrule
        %&& Search (s) & test & Search(s) & test & Search(s) & test \\ \midrule
        &&&&\textbf{Training-free}&&&\\
        NI (N=1,000)         & $X$ & $89.56\pm \z{0.147}$ & $92.55\pm 0.187$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
        NASWOT (N=1,000)     & $X$ & $89.25\pm \z{0.412}$ & $92.21\pm 0.298$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
        LogSynFlow (N=1,000) & $X$ & $89.61\pm \z{0.101}$ & $92.60\pm 0.188$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
        rk (N=1000)          & $X$ & $89.59\pm \z{0.136}$ & $92.51\pm 0.171$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
        GA-rk                & $457.54$ & $90.29\pm \z{0.149}$ & $93.27\pm0.193$ & $69.88\pm \z{0.497}$ & $70.06\pm \z{0.481}$ & $45.57\pm 0.425$ & $46.19\pm \z{0.846}$ \\ 
        SA-rk                & $682.36$ & $90.37\pm \z{0.204}$ & $93.29\pm0.182$ & $70.11\pm \z{0.457}$ & $70.32\pm \z{0.458}$ & $45.38\pm 0.499$ & $46.45\pm \z{0.687}$ \\ \bottomrule
        \end{tabular}
        \label{table:overall_sss}
          \vspace{-\baselineskip}
      \end{table*}

    \subsection{NAS-Bench-201}
    The result of NAS-Bench-201 is shown in \xtab{table:overall_201}.

@@

        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms in NAS-Bench-201.}}

@@

        \begin{tabular}{@{}lrcccccc@{}}\toprule

@@

        AREA      & $12,000$ & $91.18 \pm \z{0.43}$                & $93.95 \pm \z{0.39}$               & $71.84 \pm \z{1.21}$                 & $71.92 \pm \z{1.29}$                & $45.04 \pm 1.03$                 & $45.40 \pm 1.14$                \\
        REA       & $12,000$ & $91.08 \pm \z{0.54}$                & $93.89 \pm \z{0.50}$               & $71.69 \pm \z{1.34}$                 & $71.83 \pm \z{1.33}$                & $44.96 \pm 1.41$                 & $45.30 \pm 1.51$                \\
        RS        & $12,000$ & $90.91 \pm \z{0.33}$                & $93.67 \pm \z{0.33}$               & $70.91 \pm \z{1.04}$                 & $70.99 \pm \z{0.99}$                & $44.52 \pm 0.99$                 & $44.56 \pm 1.25$                \\
        RL        & $12,000$ & $90.87 \pm \z{0.41}$                & $93.63 \pm \z{0.36}$               & $70.62 \pm \z{1.08}$                 & $70.77 \pm \z{1.05}$                & $44.20 \pm 1.22$                 & $44.23 \pm 1.37$                \\
        BOHB      & $12,000$ & $88.47 \pm \z{1.19}$                & $91.79 \pm \z{1.11}$               & $67.18 \pm \z{2.05}$                 & $67.50 \pm \z{2.05}$                & $38.94 \pm 3.58$                 & $39.00 \pm 3.73$                \\ \midrule

@@

        RSWS      & $4,154$  & $76.95 \pm 16.74$                   & $82.60 \pm 12.10$                  & $52.51 \pm 18.33$                    & $52.93 \pm 18.32$                   & $29.76 \pm 9.50$                 & $29.16 \pm 9.61$                \\
        DARTS-V1  & $5,475$  & $39.77 \pm \z{0.00}$                & $54.30 \pm \z{0.00}$               & $15.03 \pm \z{0.00}$                 & $15.61 \pm \z{0.00}$                & $16.43 \pm 0.00$                 & $16.32 \pm 0.00$                \\
        DARTS-V2  & $16,114$ & $39.77 \pm \z{0.00}$                & $54.30 \pm \z{0.00}$               & $15.03 \pm \z{0.00}$                 & $15.61 \pm \z{0.00}$                & $16.43 \pm 0.00$                 & $16.32 \pm 0.00$                \\
